Consistency scores in text data

### 2020-07-31 outputs/documents/paper.Rmd
Updates to Word2Vec section

## Statistical Language Model

@@

## Word Embedding Models
Moved from statistical to neural network. Word embedding models works by representing words as numerical dense vectors so the neural networks can understand and process. Representing words as dense vectors has a long history, but the first neural network language model was proposed in 2013 by @bengio2003neural, and became the pioneer in word embedding models. In the work of @bengio2003neural, word embedding works by encoding the words into a feature vector. The feature vector represents different aspects of the word and each word is associated with a point in a vector space.

The words that are similar will have similar representations in a vector space. The similarity of the words, however, does not depend on their spelling or forms, but by their co-occurrence in given contexts. For example, a "cat" is more similar to a "dog" instead of a "car" because we are more likely to talk about cats and dogs in a same conversation. Therefore, the co-occurrence of "cat" and "dog" has higher probability than the co-occurrence of "cat" and a "car". In other words, the distributed representation is learned by the usage of words. This permits words that are used in similar contexts to result in having similar vector representations and their semantic meanings are captured naturally.

@@

Developed by Google, Word2Vec is a word embedding model that uses shallow neural network. While it is not a deep learning model, it turns words into a vector representations that deep neural networks can understand. It takes a corpus as its input and output a set of feature vectors that represent the words in the given corpus. @mikolov2013efficient proposed two architectures for learning distributed representations of words within the framework of Word2Vec — Continuous Bag-of-Words Model and Continuous Skip-gram Model.

Example:
>  vector("King") - vector("Man") + vector("Woman") = vector("Queen")

>>>>

## Language Model

@@

## Word Embedding Models
Turning words into numeric representations is an important step for machine to understand and process words. The most basic way to turn a word into a vector is one-hot encoding. However, with one-hot encoding, the number of dimensions depends on the size of the vocabulary in a given corpus, and can easily grow to extremely large number of dimensions. Word embedding models work by representing words as numerical dense vectors so the dimensions are reduced by representing the words by features **(Keli add citation)**. Representing words as dense vectors has a long history, but the idea of a dense embedding space for words was first explored in 2003 by @bengio2003neural, and became the prominent driver for word embedding models. In the work of @bengio2003neural, words are encoded into feature vectors that represents different aspects of the word, and each word is associated with a point in a vector space. The words that are similar will have similar representations in a vector space. The similarity of the words, however, does not depend on their spelling or forms, but by their co-occurrence in given contexts. For example, a "cat" is more similar to a "dog" instead of a "car" because we are more likely to talk about cats and dogs in a same conversation. Therefore, the co-occurrence of "cat" and "dog" has higher probability than the co-occurrence of "cat" and a "car". In other words, the distributed representation is learned by the usage of words. This permits words that are used in similar contexts to result in having similar vector representations and their semantic meanings are captured naturally.

[The word representations computed using neural networks are very interesting because the learned vectors explicitly encode many linguistic regularities and patterns. Somewhat surprisingly, many of these patterns can be represented as linear translations. For example, the result of a vector calculation vec("Madrid") - vec("Spain") + vec("France") is closer to vec("Paris") than to any other word vector.]

@@

Developed by Google, Word2Vec is a word embedding model that uses shallow neural network. While it is not a deep learning model, it turns words into a vector representations that deep neural networks can understand. It takes a corpus as its input and output a set of feature vectors that represent the words in the given corpus. @mikolov2013efficient proposed two architectures for learning distributed representations of words within the framework of Word2Vec — Continuous Bag-of-Words Model (CBOW) and Continuous Skip-gram Model. CBOW uses several surrounding words, or the context, to predict a target word. On the other hand, continuous skip-gram takes a single word as input to predict its neighbouring words. For example, consider the sentence "I think therefore I am", a famous quote by Descartes. The focus word is we want to learn the embedding is set to "therefore", and the context window is set to two which will give us the two immediate preceding words and two immediate proceeding words of the focus word. The input for the CBOW is "I, think, I, am" and the output is "therefore". In contrast, the skip-gram model will take "therefore" as the input and out "I, think, I, am" as the prediction.

Word2Vec is trained on the Google News dataset that contains 6 billion tokens and the vocabulary size is restricted to one million most common words (@mikolov2013efficient).

Word2Vec use cases:
1. Find the most similar words (**Keli add example**)
2. Calculate the similarities between a pair of words (**Keli add example**)
3. Find the odd word in a list of words (**Keli add example**)
4. Perform linear algebra to vectorized words. Example:
>  vector("King") - vector("Man") + vector("Woman") = vector("Queen")
